Postural changes mediate children's visual access to social information

### 2018-01-18 writeup-cogsci-jan14/cogsci2018_faceOnly.Rmd
typos

To formalize these observations, we fit a generalized logistic mixed-effect model to all with the presence/absence of a face on every frame as the dependent variable, and participant's age, orientation, and posture as predictors. Interactions between predictors were not included as this maximal model failed to converge. A summary of the coefficients of this model can be found in Table 3 for the MTCNN detections, though we found the same pattern of results for the OpenPose detections.  While age remained a significant predictor even when accounting for the effects of infants' posture and  orientation, it accounted for the least amount of variance. Overall, these results suggest that, instead, infants' access to faces is heavily infleunced by their own posture and theirorientation towards their caregiver.

```{r MTCNNModel, results="asis"}
tab2 <- xtable::xtable(summary(fullModelminsInt_Faces_MTCNN)$coef, digits=3,
                      caption = "Results from GLMM model prediting the presence/absence of a face (MTCNN-Faces) across the entire dataset.")

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utternace) as a function of infants's posture. Each point represents a naming instance for each child in the dataset."}
ggplot(aroundNamings, aes(x = factor(posture), y = face, color=posture)) + 
  geom_boxplot() + 
  ylab("Prop. face detections") + 
  xlab("Posture") + 
  theme_bw() 
```
## Access to Faces During Labeling Events
Finally, we analyzed how face detections changed during object labeling events as a function of infant's posture and orientation.  Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We again found that infant's posture impacted the degree to which they saw their caregiver's face during a labeling event; infants who were sitting or standing were more likely to have access to their caregiver's face.

>>>>

To formalize these observations, we fit a generalized logistic mixed-effect model to all with the presence/absence of a face on every frame as the dependent variable, and participant's age, orientation, and posture as predictors. Interactions between predictors were not included as this maximal model failed to converge. A summary of the coefficients of this model can be found in Table 3 for the MTCNN detections, though we found the same pattern of results for the OpenPose detections.  While age remained a significant predictor even when accounting for the effects of infants' posture and  orientation, it accounted for the least amount of variance. Overall, these results suggest that, instead, infants' access to faces is heavily infleunced by their own posture and their orientation towards their caregiver.

```{r MTCNNModel, results="asis"}
tab2 <- xtable::xtable(summary(fullModelminsInt_Faces_MTCNN)$coef, digits=3,
                      caption = "Results from GLMM model predicting the presence/absence of a face (MTCNN-Faces) across the entire dataset.")

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture. Each point represents a naming instance for each child in the dataset."}
ggplot(aroundNamings, aes(x = factor(posture), y = face, color=posture)) + 
  geom_boxplot() + 
  ylab("Prop. face detections") + 
  xlab("Posture") + 
  theme_bw() 
```
## Access to Faces During Labeling Events
Finally, we analyzed how face detections changed during object labeling events as a function of infant's posture and orientation.  Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We again found that infant's posture impacted the degree to which they saw their caregiver's face during a labeling event; infants who were sitting or standing were more likely to have access to their caregiver's face.

### 2018-01-18 writeup-cogsci-jan14/cogsci2018_faceOnly.tex
typos

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.846 & 0.077 & -62.682 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.061 & 2.766 & 0.006 \\ 
  postureprone & -0.513 & 0.036 & -14.045 & 0.000 \\ 
  posturesit & 0.648 & 0.034 & 18.853 & 0.000 \\ 
  posturestand & 1.005 & 0.035 & 28.402 & 0.000 \\ 
  orientationclose & 1.549 & 0.021 & 72.757 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 101.138 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model prediting the presence/absence of a face (MTCNN-Faces) across the entire dataset.} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.846 & 0.077 & -62.682 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.061 & 2.766 & 0.006 \\ 
  postureprone & -0.513 & 0.036 & -14.045 & 0.000 \\ 
  posturesit & 0.648 & 0.034 & 18.853 & 0.000 \\ 
  posturestand & 1.005 & 0.035 & 28.402 & 0.000 \\ 
  orientationclose & 1.549 & 0.021 & 72.757 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 101.138 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model prediting the presence/absence of faces (OpenPose-Faces) across the entire dataset.} 
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.847 & 0.064 & -75.303 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.075 & 2.273 & 0.023 \\ 
  postureprone & -0.513 & 0.042 & -12.326 & 0.000 \\ 
  posturesit & 0.648 & 0.039 & 16.422 & 0.000 \\ 
  posturestand & 1.005 & 0.041 & 24.721 & 0.000 \\ 
  orientationclose & 1.549 & 0.022 & 71.940 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 100.357 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model prediting the presence/absence of a face (MTCNN-Faces) across the entire dataset.} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.847 & 0.064 & -75.303 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.075 & 2.273 & 0.023 \\ 
  postureprone & -0.513 & 0.042 & -12.326 & 0.000 \\ 
  posturesit & 0.648 & 0.039 & 16.422 & 0.000 \\ 
  posturestand & 1.005 & 0.041 & 24.721 & 0.000 \\ 
  orientationclose & 1.549 & 0.022 & 71.940 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 100.357 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model prediting the presence/absence of faces (OpenPose-Faces) across the entire dataset.} 
\end{table}
